Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry

### 2017-04-14 pre_post.tex
Finish reference formatting

\bibitem[{Kingma \textit{et~al.}(2013)Kingma, Hall, \& Peters}]{Kingma2013}
Kingma, S.~A., Hall, M.~L. \& Peters A. 2013.
\newblock {Breeding synchronization facilitates extrapair mating for inbreeding
  avoidance}.
\newblock \textit{Behav. Ecol.} \textbf{24}:1390--1397.

@@

\bibitem[{Kokko \& Ots(2006)}]{Kokko2006}
Kokko, H., \& Ots, I. 2006.
\newblock {When not to avoid inbreeding}.
\newblock \textit{Evolution} \textbf{60}:467--475.
% ==================================================================================================
\bibitem[{Kuriwada et~al.(2011)Kuriwada, Kumano, Shiromoto, and
  Haraguchi}]{Kuriwada2011}
Kuriwada, T., N.~Kumano, K.~Shiromoto, and D.~Haraguchi. 2011.
\newblock {Inbreeding avoidance or tolerance? Comparison of mating behavior
  between mass-reared and wild strains of the sweet potato weevil}.
\newblock Behavioral Ecology and Sociobiology 65:1483--1489.

\bibitem[{Lande(1976)}]{Lande1976}
Lande, R. 1976.
\newblock {The maintenance of genetic variability by mutation in a polygenic
  character with linked loci}.
\newblock Genetical Research 36:221--235.

\bibitem[{Lehtonen and Kokko(2015)}]{Lehtonen2015}
Lehtonen, J., and H.~Kokko. 2015.
\newblock {Why inclusive fitness can make it adaptive to produce less fit
  extra-pair offspring}.
\newblock Proceedings of the Royal Society B 282:20142716.

\bibitem[{Levin and Lubchenco(2008)}]{Levin2008}
Levin, S.~A., and J.~Lubchenco. 2008.
\newblock {Resilience, robustness, and marine ecosystem-based management}
  58:27--32.

\bibitem[{Lihoreau et~al.(2007)Lihoreau, Zimmer, and Rivault}]{Lihoreau2007}
Lihoreau, M., C.~Zimmer, and C.~Rivault. 2007.
\newblock {Kin recognition and incest avoidance in a group-living insect}.
\newblock Behavioral Ecology 18:880--887.

\bibitem[{Liu et~al.(2014)Liu, Tu, He, Chen, and Xue}]{Liu2014}
Liu, X., X.~Tu, H.~He, C.~Chen, and F.~Xue. 2014.
\newblock {Evidence for inbreeding depression and pre-copulatory, but not post
  copulatory inbreeding avoidance in the cabbage beetle Colaphellus bowringi.}
\newblock PloS one 9:e94389.

\bibitem[{Lynch and Walsh(1998)}]{Lynch1998}
Lynch, M., and B.~Walsh. 1998.
\newblock {Genetics and Analysis of Quantitative Traits}.
\newblock Sinauer, Sunderland.

\bibitem[{Metzger et~al.(2010{\natexlab{\emph{a}}})Metzger, Bernstein,
  Hoffmeister, and Desouhant}]{Metzger2010}
Metzger, M., C.~Bernstein, T.~S. Hoffmeister, and E.~Desouhant.
  2010{\natexlab{\emph{a}}}.
\newblock {Does kin recognition and sib-mating avoidance limit the risk of
  genetic incompatibility in a parasitic wasp?}
\newblock PLoS One 5:1--6.

\bibitem[{Metzger et~al.(2010{\natexlab{\emph{b}}})Metzger, Fischbein, Auguste,
  Fauvergue, Bernstein, and Desouhant}]{Metzger2010a}
Metzger, M., D.~Fischbein, A.~Auguste, X.~Fauvergue, C.~Bernstein, and
  E.~Desouhant. 2010{\natexlab{\emph{b}}}.
\newblock {Synergy in information use for mate finding: Demonstration in a
  parasitoid wasp}.
\newblock Animal Behaviour 79:1307--1315.

\bibitem[{Mills and Smouse(1994)}]{Mills1994}
Mills, L.~S., and P.~E. Smouse. 1994.
\newblock {Demographic consequences of inbreeding in remnant populations}.
\newblock American Naturalist 144:412--431.

\bibitem[{Morton et~al.(1956)Morton, Crow, and Muller}]{Morton1956}
Morton, N.~E., J.~F. Crow, and H.~J. Muller. 1956.
\newblock {An estimate of the mutational damage in man from data on
  consanguineous marriages}.
\newblock Proceedings of the National Academy of Sciences 42:855--863.

\bibitem[{Nowak et~al.(1997)Nowak, Boerlijst, Cooke, and {Maynard
  Smith}}]{Nowak1997}
Nowak, M.~A., M.~C. Boerlijst, J.~Cooke, and J.~{Maynard Smith}. 1997.
\newblock {Evolution of genetic redundancy}.
\newblock Nature 388:167--171.

\bibitem[{Park and Friston(2013)}]{Park2013}
Park, H.~J., and K.~J. Friston. 2013.
\newblock {Structural and functional brain networks: from connections to
  cognition.}
\newblock Science 342:1238411.

\bibitem[{Parker(1979)}]{Parker1979}
Parker, G.~A. 1979.
\newblock {Sexual selection and sexual conflict}.
\newblock Pages 123--166 \emph{in} M.~S. Blum and N.~A. Blum, eds. Sexual
  selection and reproductive competition in insects. Academic Press, Inc, New
  York.

\bibitem[{Parker(2006)}]{Parker2006}
---{}---{}---. 2006.
\newblock {Sexual conflict over mating and fertilization: an overview}.
\newblock Philosophical Transactions of the Royal Society B 361:235--259.

\bibitem[{Pizzari et~al.(2004)Pizzari, L{\o}vlie, and Cornwallis}]{Pizzari2004}
Pizzari, T., H.~L{\o}vlie, and C.~K. Cornwallis. 2004.
\newblock {Sex-specific, counteracting responses to inbreeding in a bird}.
\newblock Proceedings of The Royal Society B 271:2115--2121.

\bibitem[{Pomiankowski(1987)}]{Pomiankowski1987}
Pomiankowski, A. 1987.
\newblock {The costs of choice in sexual selection}.
\newblock Journal of Theoretical Biology 128:195--218.

\bibitem[{Potts et~al.(1991)Potts, Manning, and Wakeland}]{Potts1991}
Potts, W.~K., C.~J. Manning, and E.~K. Wakeland. 1991.
\newblock {Mating patterns in seminatural populations of mice influenced by MHC
  genotype}.
\newblock Nature 352:619--621.

\bibitem[{Price and Friston(2002)}]{Price2002}
Price, C.~J., and K.~J. Friston. 2002.
\newblock {Degeneracy and cognitive anatomy}.
\newblock Trends in Cognitive Sciences 6:416--421.

\bibitem[{Pusey and Wolf(1996)}]{Pusey1996}
Pusey, A., and M.~Wolf. 1996.
\newblock {Inbreeding avoidance in animals}.
\newblock Trends in Ecology {\&} Evolution 5347:298--301.

\bibitem[{Reeve(2000)}]{Reeve2000}
Reeve, J.~P. 2000.
\newblock {Predicting long-term response to selection}.
\newblock Genetical Research 75:83--94.

\bibitem[{Reid(2015)}]{Reid2015a}
Reid, J.~M. 2015.
\newblock {What can we really say about relatedness and extrapair paternity: a
  comment on Arct et al}.
\newblock Behavioral Ecology 00:1--2.

\bibitem[{Reid et~al.(2015{\natexlab{\emph{a}}})Reid, Arcese, Keller, Germain,
  Duthie, Losdat, Wolak, and Nietlisbach}]{Reid2014}
Reid, J.~M., P.~Arcese, L.~F. Keller, R.~R. Germain, A.~B. Duthie, S.~Losdat,
  M.~E. Wolak, and P.~Nietlisbach. 2015{\natexlab{\emph{a}}}.
\newblock {Quantifying inbreeding avoidance through extra-pair reproduction}.
\newblock Evolution 69:59--74.

\bibitem[{Reid et~al.(2015{\natexlab{\emph{b}}})Reid, Duthie, Wolak, and
  Arcese}]{Reid2015}
Reid, J.~M., A.~B. Duthie, M.~E. Wolak, and P.~Arcese.
  2015{\natexlab{\emph{b}}}.
\newblock {Demographic mechanisms of inbreeding adjustment through extra-pair
  reproduction}.
\newblock Journal of Animal Ecology 84:1029--1040.

\bibitem[{Roberts et~al.(2015)Roberts, Evison, Baer, and Hughes}]{Roberts2015a}
Roberts, K.~E., S.~E.~F. Evison, B.~Baer, and W.~O.~H. Hughes. 2015.
\newblock {The cost of promiscuity: sexual transmission of Nosema
  microsporidian parasites in polyandrous honey bees}.
\newblock Scientific Reports 5:10982.

\bibitem[{Roff(1996)}]{Roff1996}
Roff, D.~A. 1996.
\newblock {The evolution of threshold traits in animals}.
\newblock The Quarterly Review of Biology 71:3--35.

\bibitem[{Roff(1998)}]{Roff1998}
---{}---{}---. 1998.
\newblock {Evolution of threshold traits: the balance between directional
  selection, drift and mutation}.
\newblock Heredity 80:25--32.

\bibitem[{Ronkainen and Ylonen(1994)}]{Ronkainen1994}
Ronkainen, H., and H.~Ylonen. 1994.
\newblock {Behaviour of cyclic bank voles under risk of mustelid predation: Do
  females avoid copulations?}
\newblock Oecologia 97:377--381.

\bibitem[{Rowe(1988)}]{Rowe1988}
Rowe, L. 1988.
\newblock {Cost of mating for female insects: risk of predation in Photinus
  collustrans (Coleoptera: Lampyridae)}.
\newblock American Naturalist 121:139--142.

\bibitem[{Rowe et~al.(1994)Rowe, Arnqvist, Sih, and Krupa}]{Rowe1994}
Rowe, L., G.~Arnqvist, A.~Sih, and J.~J. Krupa. 1994.
\newblock {Sexual conflict and the evolutionary ecology of mating patterns:
  water striders as a model system}.
\newblock Trends in Ecology {\&} Evolution 9:289--293.

\bibitem[{Simmons et~al.(2006)Simmons, Beveridge, Wedell, and
  Tregenza}]{Simmons2006}
Simmons, L.~W., M.~Beveridge, N.~Wedell, and T.~Tregenza. 2006.
\newblock {Postcopulatory inbreeding avoidance by female crickets only revealed
  by molecular markers}.
\newblock Molecular Ecology 15:3817--3824.

\bibitem[{Suraci et~al.(2017)Suraci, Clinchy, and Zanette}]{Suraci2017}
Suraci, J.~P., M.~Clinchy, and L.~Y. Zanette. 2017.
\newblock {Do large carnivores and mesocarnivores have redundant impacts on
  intertidal prey?}
\newblock PLoS One 12:e0170255.

\bibitem[{Szulkin et~al.(2013)Szulkin, Stopher, Pemberton, and
  Reid}]{Szulkin2012}
Szulkin, M., K.~V. Stopher, J.~M. Pemberton, and J.~M. Reid. 2013.
\newblock {Inbreeding avoidance, tolerance, or preference in animals?}
\newblock Trends in Ecology {\&} Evolution 28:205--211.

\bibitem[{Tan et~al.(2012)Tan, L{\o}vlie, Pizzari, and Wigby}]{Tan2012}
Tan, C. K.~W., H.~L{\o}vlie, T.~Pizzari, and S.~Wigby. 2012.
\newblock {No evidence for precopulatory inbreeding avoidance in Drosophila
  melanogaster}.
\newblock Animal Behaviour 83:1433--1441.

\bibitem[{Tregenza and Wedell(2002)}]{Tregenza2002}
Tregenza, T., and N.~Wedell. 2002.
\newblock {Polyandrous females avoid costs of inbreeding}.
\newblock Nature 415:71--73.

\bibitem[{Tuni et~al.(2013)Tuni, Beveridge, and Simmons}]{Tuni2013}
Tuni, C., M.~Beveridge, and L.~W. Simmons. 2013.
\newblock {Female crickets assess relatedness during mate guarding and bias
  storage of sperm towards unrelated males}.
\newblock Journal of Evolutionary Biology 26:1261--1268.

\bibitem[{Varian-Ramos and Webster(2012)}]{Varian-Ramos2012}
Varian-Ramos, C.~W., and M.~S. Webster. 2012.
\newblock {Extrapair copulations reduce inbreeding for female red-backed
  fairy-wrens, Malurus melanocephalus}.
\newblock Animal Behaviour 83:857--864.

\bibitem[{Whitacre and Bender(2010)}]{Whitacre2010}
Whitacre, J., and A.~Bender. 2010.
\newblock {Degeneracy: A design principle for achieving robustness and
  evolvability}.
\newblock Journal of Theoretical Biology 263:143--153.

\bibitem[{Whitacre(2010)}]{Whitacre2010a}
Whitacre, J.~M. 2010.
\newblock {Degeneracy: a link between evolvability, robustness and complexity
  in biological systems}.
\newblock Theoretical Biology and Medical Modelling 7:6.

\bibitem[{Zeh and Zeh(1997)}]{Zeh1997}
Zeh, J.~A., and D.~W. Zeh. 1997.
\newblock {The evolution of polyandry II: post-copulatory defenses against
  genetic incompatibility}.
\newblock Proceedings of the Royal Society B 264:69--75.

>>>>

\bibitem[{Kingma \textit{et~al.}(2013)Kingma, Hall \& Peters}]{Kingma2013}
Kingma, S.~A., Hall, M.~L. \& Peters A. 2013.
\newblock {Breeding synchronization facilitates extrapair mating for inbreeding
  avoidance}.
\newblock \textit{Behav. Ecol.} \textbf{24}:1390--1397.

@@

\bibitem[{Kokko \& Ots(2006)}]{Kokko2006}
Kokko, H., \& Ots, I. 2006.
\newblock {When not to avoid inbreeding}.
\newblock \textit{Evolution} \textbf{60}:467--475.
% ==================================================================================================
\bibitem[{Kuriwada \textit{et~al.}(2011)Kuriwada, Kumano, Shiromoto \&
  Haraguchi}]{Kuriwada2011}
Kuriwada, T., Kumano, N., Shiromoto, K. \& Haraguchi, D. 2011.
\newblock {Inbreeding avoidance or tolerance? Comparison of mating behavior
  between mass-reared and wild strains of the sweet potato weevil}.
\newblock \textit{Behav. Ecol. Sociobiol.} \textbf{65}:1483--1489.

\bibitem[{Lande(1976)}]{Lande1976}
Lande, R. 1976.
\newblock {The maintenance of genetic variability by mutation in a polygenic
  character with linked loci}.
\newblock \textit{Genet. Res.} \textbf{36}:221--235.

\bibitem[{Lehtonen \& Kokko(2015)}]{Lehtonen2015}
Lehtonen, J. \& Kokko, H. 2015.
\newblock {Why inclusive fitness can make it adaptive to produce less fit
  extra-pair offspring}.
\newblock \textit{Proc. Biol. Sci.} \textbf{282}:20142716.

\bibitem[{Levin \& Lubchenco(2008)}]{Levin2008}
Levin, S.~A. \& Lubchenco, J. 2008.
\newblock {Resilience, robustness, and marine ecosystem-based management}
\newblock \textit{BioScience} \textbf{58}:27--32.

\bibitem[{Lihoreau \textit{et~al.}(2007)Lihoreau, Zimmer \& Rivault}]{Lihoreau2007}
Lihoreau, M., Zimmer, C. \& Rivault, C. 2007.
\newblock {Kin recognition and incest avoidance in a group-living insect}.
\newblock \textit{Behav. Ecol.} \textbf{18}:880--887.

\bibitem[{Liu \textit{et~al.}(2014)Liu, Tu, He, Chen \& Xue}]{Liu2014}
Liu, X., Tu, X., He, H., Chen, C. \& Xue, F. 2014.
\newblock {Evidence for inbreeding depression and pre-copulatory, but not post
  copulatory inbreeding avoidance in the cabbage beetle \textit{Colaphellus bowringi}.}
\newblock \textit{PloS one} \textbf{9}:e94389.

\bibitem[{Lynch \& Walsh(1998)}]{Lynch1998}
Lynch, M. \& Walsh, B. 1998.
\newblock {\textit{Genetics and Analysis of Quantitative Traits}}.
\newblock Sinauer, Sunderland.

\bibitem[{Metzger \textit{et~al.}(2010{\natexlab{\emph{a}}})Metzger, Bernstein,
  Hoffmeister \& Desouhant}]{Metzger2010}
Metzger, M., Bernstein, C., Hoffmeister, T.~S. \& Desouhant, E.
  2010{\natexlab{\emph{a}}}.
\newblock {Does kin recognition and sib-mating avoidance limit the risk of
  genetic incompatibility in a parasitic wasp?}
\newblock \textit{PLoS One} \textbf{5}:1--6.

\bibitem[{Metzger \textit{et~al.}(2010{\natexlab{\emph{b}}})Metzger, Fischbein, Auguste,
  Fauvergue, Bernstein \& Desouhant}]{Metzger2010a}
Metzger, M., Fischbein, D., Auguste, A., Fauvergue, X., Bernstein, C., \&
  Desouhant, E. 2010{\natexlab{\emph{b}}}.
\newblock {Synergy in information use for mate finding: Demonstration in a
  parasitoid wasp}.
\newblock \textit{Anim. Behav.} 79:1307--1315.

\bibitem[{Mills \& Smouse(1994)}]{Mills1994}
Mills, L.~S. \& Smouse, P.~E. 1994.
\newblock {Demographic consequences of inbreeding in remnant populations}.
\newblock \textit{Am. Nat.} \textbf{144}:412--431.

\bibitem[{Morton et~al.(1956)Morton, Crow \& Muller}]{Morton1956}
Morton, N.~E., Crow, J.~F., \& Muller, H.~J. 1956.
\newblock {An estimate of the mutational damage in man from data on
  consanguineous marriages}.
\newblock \textit{Proc. Natl. Acad. Sci. USA} \textbf{42}:855--863.

\bibitem[{Nowak \textit{et~al.}(1997)Nowak, Boerlijst, Cooke, \& {Maynard
  Smith}}]{Nowak1997}
Nowak, M.~A., Boerlijst, M.~C., Cooke, J. \& {Maynard Smith}, J. 1997.
\newblock {Evolution of genetic redundancy}.
\newblock \textit{Nature} \textbf{388}:167--171.

\bibitem[{Park \& Friston(2013)}]{Park2013}
Park, H.~J. \& Friston, K.~J. 2013.
\newblock {Structural and functional brain networks: from connections to
  cognition.}
\newblock \textit{Science} \textbf{342}:1238411.

\bibitem[{Parker(1979)}]{Parker1979}
Parker, G.~A. 1979.
\newblock {Sexual selection and sexual conflict}.
\newblock Pages 123--166 \emph{in} M.~S. Blum \& N.~A. Blum, eds. \textit{Sexual
  selection and reproductive competition in insects}. Academic Press, Inc, New
  York.

\bibitem[{Parker(2006)}]{Parker2006}
Parker, G.~A. 2006.
\newblock {Sexual conflict over mating and fertilization: an overview}.
\newblock \textit{Phil. Trans. R. Soc. Lond. B Biol. Sci.} \textbf{361}:235--259.

\bibitem[{Pizzari \textit{et~al.}(2004)Pizzari, L{\o}vlie, \& Cornwallis}]{Pizzari2004}
Pizzari, T., L{\o}vlie, H. \& Cornwallis, C.~K. 2004.
\newblock {Sex-specific, counteracting responses to inbreeding in a bird}.
\newblock \textit{Proc. Biol. Sci.} \textbf{271}:2115--2121.

\bibitem[{Pomiankowski(1987)}]{Pomiankowski1987}
Pomiankowski, A. 1987.
\newblock {The costs of choice in sexual selection}.
\newblock \textit{J. Theor. Biol.} \textbf{128}:195--218.

\bibitem[{Potts \textit{et~al.}(1991)Potts, Manning \& Wakeland}]{Potts1991}
Potts, W.~K., Manning, C.~J. \& Wakeland, E.~K. 1991.
\newblock {Mating patterns in seminatural populations of mice influenced by MHC
  genotype}.
\newblock \textit{Nature} \textbf{352}:619--621.

\bibitem[{Price \& Friston(2002)}]{Price2002}
Price, C.~J. \& Friston, K.~J. 2002.
\newblock {Degeneracy and cognitive anatomy}.
\newblock \textit{Trends Cogn. Sci.} \textbf{6}:416--421.

\bibitem[{Pusey \& Wolf(1996)}]{Pusey1996}
Pusey, A., \& Wolf, M. 1996.
\newblock {Inbreeding avoidance in animals}.
\newblock \textit{Trends Ecol. Evol.} \textbf{5347}:298--301.

\bibitem[{Reeve(2000)}]{Reeve2000}
Reeve, J.~P. 2000.
\newblock {Predicting long-term response to selection}.
\newblock \textit{Genet. Res.} \textbf{75}:83--94.

\bibitem[{Reid(2015)}]{Reid2015a}
Reid, J.~M. 2015.
\newblock {What can we really say about relatedness and extrapair paternity: a
  comment on Arct \textit{et al}}.
\newblock \textit{Behav. Ecol.} \textbf{26}:969--970.

\bibitem[{Reid \textit{et~al.}(2015{\natexlab{\emph{a}}})Reid, Arcese, Keller, Germain,
  Duthie, Losdat, Wolak \& Nietlisbach}]{Reid2014}
Reid, J.~M., Arcese, P., Keller, L.~F., Germain, R.~R., Duthie, A.~B., Losdat, S.,
  Wolak, M.~E. \& Nietlisbach, P. 2015{\natexlab{\emph{a}}}.
\newblock {Quantifying inbreeding avoidance through extra-pair reproduction}.
\newblock \textit{Evolution} \textbf{69}:59--74.

\bibitem[{Reid \textit{et~al.}(2015{\natexlab{\emph{b}}})Reid, Duthie, Wolak \&
  Arcese}]{Reid2015}
Reid, J.~M., Duthie, A.~B., Wolak, M.~E. \& Arcese, P.
  2015{\natexlab{\emph{b}}}.
\newblock {Demographic mechanisms of inbreeding adjustment through extra-pair
  reproduction}.
\newblock \textit{J. Anim. Ecol.} \textbf{84}:1029--1040.

\bibitem[{Roberts \textit{et~al.}(2015)Roberts, Evison, Baer \& Hughes}]{Roberts2015a}
Roberts, K.~E., Evison, S.~E.~F., Baer, B. \& Hughes, W.~O.~H. 2015.
\newblock {The cost of promiscuity: sexual transmission of \textit{Nosema
  microsporidian} parasites in polyandrous honey bees}.
\newblock \textit{Sci. Rep.} \textbf{5}:10982.

\bibitem[{Roff(1996)}]{Roff1996}
Roff, D.~A. 1996.
\newblock {The evolution of threshold traits in animals}.
\newblock \textit{Q. Rev. Biol.} \textbf{71}:3--35.

\bibitem[{Roff(1998)}]{Roff1998}
Roff, D.~A. 1998.
\newblock {Evolution of threshold traits: the balance between directional
  selection, drift and mutation}.
\newblock \textit{Heredity} \textbf{80}:25--32.

\bibitem[{Ronkainen \& Ylonen(1994)}]{Ronkainen1994}
Ronkainen, H. \& Ylonen, H. 1994.
\newblock {Behaviour of cyclic bank voles under risk of mustelid predation: Do
  females avoid copulations?}
\newblock \textit{Oecologia} \textbf{97}:377--381.

\bibitem[{Rowe(1988)}]{Rowe1988}
Rowe, L. 1988.
\newblock {Cost of mating for female insects: risk of predation in \textit{Photinus
  collustrans} (Coleoptera: Lampyridae)}.
\newblock \textit{Am. Nat.} \textbf{121}:139--142.

\bibitem[{Rowe \textit{et~al.}(1994)Rowe, Arnqvist, Sih \& Krupa}]{Rowe1994}
Rowe, L., Arnqvist, G., Sih, A. \& Krupa, J.~J. 1994.
\newblock {Sexual conflict and the evolutionary ecology of mating patterns:
  water striders as a model system}.
\newblock \textit{Trends Ecol. Evol.} \textbf{9}:289--293.

\bibitem[{Simmons \textit{et~al.}(2006)Simmons, Beveridge, Wedell \&
  Tregenza}]{Simmons2006}
Simmons, L.~W., Beveridge, M., Wedell, N. \& Tregenza, T. 2006.
\newblock {Postcopulatory inbreeding avoidance by female crickets only revealed
  by molecular markers}.
\newblock \textit{Mol. Ecol.} \textbf{15}:3817--3824.

\bibitem[{Suraci \textit{et~al.}(2017)Suraci, Clinchy \& Zanette}]{Suraci2017}
Suraci, J.~P., Clinchy, M. \& Zanette, L.~Y. 2017.
\newblock {Do large carnivores and mesocarnivores have redundant impacts on
  intertidal prey?}
\newblock \textit{PLoS One} \textbf{12}:e0170255.

\bibitem[{Szulkin \textit{et~al.}(2013)Szulkin, Stopher, Pemberton \&
  Reid}]{Szulkin2012}
Szulkin, M., Stopher, K.~V., Pemberton, J.~M. \& Reid, J.~M. 2013.
\newblock {Inbreeding avoidance, tolerance, or preference in animals?}
\newblock \textit{Trends Ecol. Evol.} \textbf{28}:205--211.

\bibitem[{Tan \textit{et~al.}(2012)Tan, L{\o}vlie, Pizzari \& Wigby}]{Tan2012}
Tan, C. K.~W., L{\o}vlie, H., Pizzari, T. \& Wigby, S. 2012.
\newblock {No evidence for precopulatory inbreeding avoidance in \textit{Drosophila
  melanogaster}}.
\newblock \textit{Anim. Behav.} \textbf{83}:1433--1441.

\bibitem[{Tregenza \& Wedell(2002)}]{Tregenza2002}
Tregenza, T. \& Wedell, N. 2002.
\newblock {Polyandrous females avoid costs of inbreeding}.
\newblock \textit{Nature} \textbf{415}:71--73.

\bibitem[{Tuni \textit{et~al.}(2013)Tuni, Beveridge \& Simmons}]{Tuni2013}
Tuni, C., Beveridge, M. \& Simmons, L.~W. 2013.
\newblock {Female crickets assess relatedness during mate guarding and bias
  storage of sperm towards unrelated males}.
\newblock \textit{J. Evol. Biol.} \textbf{26}:1261--1268.

\bibitem[{Varian-Ramos \& Webster(2012)}]{Varian-Ramos2012}
Varian-Ramos, C.~W. \& Webster, M.~S. 2012.
\newblock {Extrapair copulations reduce inbreeding for female red-backed
  fairy-wrens, \textit{Malurus melanocephalus}}.
\newblock \textit{Anim. Behav.} \textbf{83}:857--864.

\bibitem[{Whitacre \& Bender(2010)}]{Whitacre2010}
Whitacre, J. \& Bender, A. 2010.
\newblock {Degeneracy: A design principle for achieving robustness and
  evolvability}.
\newblock \textit{J. Theor Biol.} \textbf{263}:143--153.

\bibitem[{Whitacre(2010)}]{Whitacre2010a}
Whitacre, J.~M. 2010.
\newblock {Degeneracy: a link between evolvability, robustness and complexity
  in biological systems}.
\newblock \textit{Theor. Biol. Med. Model.} \textbf{7}:6.

\bibitem[{Zeh \& Zeh(1997)}]{Zeh1997}
Zeh, J.~A. \& Zeh, D.~W. 1997.
\newblock {The evolution of polyandry II: post-copulatory defenses against
  genetic incompatibility}.
\newblock \textit{Proc. Biol. Sci.} \textbf{264}:69--75.
